\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[
margin=1in,
includefoot,
footskip=30pt,
]{geometry}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PF is machine readable/ATS parsable
\pdfgentounicode=1

%%% CUSTOM COMMANDS %%%

% Bolded Text: Text
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

% Text
\newcommand{\resumeItemTwo}[1]{
	\item\small{
		#1 \vspace{-2pt}}
}

% Text: Text
\newcommand{\resumeItemThree}[2]{
	\item\small{
		#1: #2 \vspace{-2pt}}
}

% Bold Title 					Text
% Itacliciszed Text				Italicized Text
\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
	\end{tabular*}\vspace{-5pt}
}

%% Title | Text
\newcommand{\resumeSubheadingTwo}[2]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} \rule[-0.4ex]{0.1ex}{1.2em} #2 \\
	\end{tabular*}\vspace{-5pt}
}

% Bold Title 					Text
% Italicized Text				Italicized Text
% Italicized Text
\newcommand{\resumeSubheadingThree}[5]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
		\textit{#5} & \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
	%%% Heading %%%
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{\href{https://www.ktm-p.net/}{\Large Michael Pham}} & Email: \href{mailto:ktmpham@berkeley.edu}{ktmpham@berkeley.edu}\\
		\href{https://www.ktm-p.net/}{ktm-p.net} & 
		Mobile: \href{tel:+19169680563}{(916)-968-0563} \\
	\end{tabular*}
	
	%%% Education %%%
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheadingThree
	{University of California, Berkeley}{Berkeley, CA}
	{B.A. in Computer Science and Mathematics}{Aug 2022 -- Present}
	{Minor in Data Science}
	\resumeItemListStart
	\resumeItemThree{GPA}{3.86}
	\resumeItemTwo{Member of Upsilon Pi Epsilon Honor Society}
	\resumeItemTwo{EECS Honors Program}
	\resumeItemTwo{Dean's List}
	\resumeItemListEnd
	\resumeSubHeadingListEnd
	
	%%% Work Experience %%%
	\section{Teaching Experience}
	\resumeSubHeadingListStart
	\resumeSubheading{River City High School}{West Sacramento, CA}{Teaching Assistant}{Aug 2021 -- May 2022}
	\resumeItemListStart
	\resumeItemTwo{Worked as a student teaching assistant for school's AP Calculus course.}
	\resumeItemTwo{Taught some classes, presenting key concepts in a clear and concise manner to students, along with working through examples to help deepen their understanding of the material.}
	\resumeItemTwo{Helped design assignments such as in-class work, homework, and exam problems to reinforce core ideas.}
	\resumeItemTwo{Graded assignments from students and offered clear explanations on areas to improve upon.}
	\resumeItemListEnd
	
	\resumeSubheading{River City High School}{West Sacramento, CA}{After-school Tutor}{Aug 2019 -- May 2022}
	\resumeItemListStart
	\resumeItemTwo{Volunteer tutor for mathematics, ranging from Algebra 1 to AP Calculus BC and AP Statistics.}
	\resumeItemTwo{Clearly explained core concepts to students and provided help on assignments.}
	\resumeItemListEnd
	
	\resumeSubheading{Self-Employed}{West Sacramento, CA}{Calculus Tutor}{June 2025 -- Present}
	\resumeItemListStart
	\resumeItemTwo{Private tutor for Calculus I and II.}
	\resumeItemTwo{Create lessons tailored to individual students' needs. Clearly explain and reinforce key concepts.}
	\resumeItemListEnd
	\resumeSubHeadingListEnd
	
	%%% Projects %%%
	\section{Projects}
	\resumeSubHeadingListStart
	
	\resumeSubheadingTwo
	{Audio Analyzer and Visualizer}{Java, Processing}
	\resumeItemListStart
	\resumeItemTwo{Displays different representations of audio, including waveform and polar graphs, alongside a responsive visualizer.}
	\resumeItemTwo{Implemented a Discrete Fourier Transform algorithm, along with smoothing the RDFT.}
	\resumeItemTwo{Includes a beat detection feature by observing the audio's level and seeing if there's a marginal difference.}
	\resumeItemTwo{Created 3D objects that moved, rotated, and changed size and color based on audio frequency levels.}
	\resumeItemTwo{Created moving 3D terrain using Perlin Noise mapped to audio frequencies, moving based on frequency values.}
	\resumeItemListEnd
	
	\resumeSubheadingTwo
	{Terminal ASCII Art Generator}{Python, NumPy, Pillow}
	\resumeItemListStart
	\resumeItemTwo{Created program to convert an image to ASCII.}
	\resumeItemTwo{Utilized Pillow to extract pixel information, then performed transformations to get intensity information and map to corresponding ASCII character.}
	\resumeItemTwo{Includes limited set of colors usable by all terminals. Determined best-matching color to use with linear algebra.}
	\resumeItemTwo{Implemented Sobel filter for edge-detection to further refine the resulting image.}
	\resumeItemListEnd
	\resumeSubHeadingListEnd
	
	%%% Skills %%%
	\section{Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Programming Languages}
	{C, Golang, Java, MATLAB, Python, R, RISC-V, Scheme, Snap, SQL}
	\resumeSubItem{Frameworks/Libraries}{Matplotlib, Numpy, Pandas, Plotly, PyTorch, scikit-learn, Seaborn, TensorFlow}
	\resumeSubItem{Tools}{Docker, gdb, git, Logism, Valgrind}
	\resumeSubItem{Mathematics}{Abstract Algebra, Algorithms, Complexity Theory, Cryptography, Discrete Mathematics, Linear Algebra, Linear Programming, Logic, Numerical Analysis, Real Analysis}
	\resumeItem{Other}{Bilingual (English/Vietnamese), Public Speaking, LaTeX, TikZ}
	\resumeSubHeadingListEnd
\end{document}