\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[
	margin=1in,
	includefoot,
	footskip=30pt,
]{geometry}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PF is machine readable/ATS parsable
\pdfgentounicode=1

%%% CUSTOM COMMANDS %%%

% Bolded Text: Text
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

% Text
\newcommand{\resumeItemTwo}[1]{
	\item\small{
		#1 \vspace{-2pt}}
}

% Text: Text
\newcommand{\resumeItemThree}[2]{
	\item\small{
		#1: #2 \vspace{-2pt}}
}

% Bold Title 					Text
% Itacliciszed Text				Italicized Text
\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}

%% Title | Text
\newcommand{\resumeSubheadingTwo}[2]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} \rule[-0.4ex]{0.1ex}{1.2em} #2 \\
	\end{tabular*}\vspace{-5pt}
}

% Bold Title 					Text
% Italicized Text				Italicized Text
% Italicized Text
\newcommand{\resumeSubheadingThree}[5]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{\small #4} \\
		\textit{#5} & \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
	%%% Heading %%%
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{\href{https://ktm-p.net}{\Large Michael Pham}} & Email: \href{mailto:ktmpham@berkeley.edu}{ktmpham@berkeley.edu}\\
		\href{https://ktm-p.net}{ktm-p.net} & 
		Mobile: \href{tel:+19169680563}{(916)-968-0563} \\
	\end{tabular*}
	
	%%% Education %%%
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheadingThree
	{University of California, Berkeley}{Berkeley, CA}
	{B.A. in Computer Science and Mathematics}{Aug 2022 -- Present}{Minor in Data Science}
	\resumeItemListStart
	\resumeItemThree{GPA}{\small 3.85}
	\resumeItemTwo{\small Member of Upsilon Pi Epsilon Honor Society}
	\resumeItemTwo{Dean's List, Honors to Date}
	\resumeItemListEnd
	\resumeSubHeadingListEnd
	
		%%% Work Experience %%%
	\section{Professional Experience}
	\resumeSubHeadingListStart
	\resumeSubheading{Self-Employed}{West Sacramento, CA}{Calculus Tutor}{June 2025 -- Present}
	\resumeItemListStart
	\resumeItemTwo{Private tutor for Calculus I and II.}
	\resumeItemTwo{Created lessons tailored to individual students' needs.}
	\resumeItemTwo{Explained and reinforced key concepts through examples and practice problems for students.}
	\resumeItemListEnd
	\resumeSubHeadingListEnd
	
	%%% Projects %%%
	\section{Projects}
	\resumeSubHeadingListStart
	
	\resumeSubheadingTwo
	{Audio Analyzer and Visualizer}{Java, Processing}
	\resumeItemListStart
	\resumeItemTwo{Displays different representations of audio, including waveform and polar graphs, alongside a responsive visualizer.}
	\resumeItemTwo{Implemented (smoothed) DFT and FFT to extract frequency information and create audio-responsive visuals.}
	\resumeItemTwo{Implemented beat detection by comparing the audio's level to previous in stack.}
	\resumeItemListEnd
	
%	\resumeSubheadingTwo
%	{Optimizing Convolutions}{C, OpenMP, OpenMPI, SIMD}
%	\resumeItemListStart
%	\resumeItemTwo{Implemented a na\"ive 2D Convolution algorithm and optimized it.}
%	\resumeItemTwo{Optimizations include efficient cache usage, parallel programming, vectorizing operations, loop unrolling, and working with pointers. Achieved around a 50x speedup.}
%	\resumeItemListEnd
	
	\resumeSubheadingTwo
	{A Secure File Sharing System}{Golang}
	\resumeItemListStart
	\resumeItemTwo{Designed and implemented a secure file sharing system using cryptographic library functions.}
	\resumeItemTwo{Implemented file creation, appending, sharing, and deletion among multiple users across multiple devices.}
	\resumeItemTwo{Utilized symmetric encryption, HMACs, and digital signatures to ensure security.}
	\resumeItemTwo{Extensively tested implementation, writing over three thousand lines of test code.}
	\resumeItemListEnd
	
	\resumeSubheadingTwo
	{MapReduce}{Rust}
	\resumeItemListStart
	\resumeItemTwo{Implemented a MapReduce coordinator in Rust which distributed map and reduce tasks to workers.}
	\resumeItemTwo{Ensured memory and thread safety for effective parallelization.}
	\resumeItemListEnd
	
	\resumeSubheadingTwo
	{Implementing the GGH Cryptosystem}{Python}
	\resumeItemListStart
	\resumeItemTwo{Wrote a paper discussing the mathematics behind the GGH Encryption Scheme and implemented it in Python.}
	\resumeItemTwo{Implemented proper key generation, encryption, and decryption}
	\resumeItemTwo{Minimize errors by switching to symPy. Optimized key generation to handle larger dimensions.}
	\resumeItemListEnd
	
	\resumeSubheadingTwo
	{Rasterizer}{C++}
	\resumeItemListStart
	\resumeItemTwo{Implemented a rasterizer with features like drawing triangles, supersampling, and texture mapping.}
	\resumeItemTwo{Created a triangle rasterizer and optimized it by removing redundant operations and direct edge computations.}
	\resumeItemTwo{Antialiasing via supersampling. Implemented jitter sampling as well to reduce issues such as the Moire effect.}
	\resumeItemTwo{Introduced pixel sampling and also level sampling with mipmaps for texture mapping.}
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	
	%%% Coursework %%%
	\section{Relevant Coursework}
	\resumeSubHeadingListStart
	\resumeSubItem{Computer Science}
	{Data Structures, Discrete Mathematics, Computer Security, Efficient Algorithms and Intractable Problems, Computability and Complexity}
	\resumeSubItem{Mathematics}{Introduction to Analysis, Abstract Algebra, Abstract Linear Algebra, Cryptography, Numerical Analysis, Programming for Mathematical Applications}
	\resumeSubHeadingListEnd
	
	%%% Skills %%%
	\section{Technical Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Programming Languages}
	{C, C++, Golang, Java, Julia, MATLAB, Python, R, RISC-V, Scheme, SQL}
	\resumeSubItem{Frameworks/Libraries}{Matplotlib, Numpy, OpenMP, Pandas, PyTorch, scikit-learn, Seaborn, TensorFlow}
	\resumeSubItem{Tools}{Docker, gdb, git, Logism, LaTeX, Valgrind}
	\resumeSubHeadingListEnd
\end{document}